Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-16 robdml.tex
p8

Our method overwhelmingly outperforms the previous methods in terms of the
overall performance. Namely, our method achieves the highest ERS with a very
low decrement in R@1 under a fixed training cost.
%
HM[$\mathcal{R},\mathcal{M}$] or HM[$\mathcal{R},g_\mathsf{LGA}$] can reach an
even higher ERS, but are excluded from comparison due to significant drop in
R@1.
%

@@

It \emph{should} be noted that the $L_\text{ICS}$ term improves 
robustness against most attacks involved in ERS, but also increases the
tendency to collapse (observed during TMA~\cite{flowertower} attack --
high cosine similarity between two arbitrary benign examples).
%
In some cases (\eg, on SOP), the performance drop \emph{w.r.t} TMA may
neutralize the ERS gain from other attacks.

>>>>

Our method overwhelmingly outperforms the previous methods in terms of the
overall performance. Namely, our method efficiently reaches the highest ERS with a very
low decrement in R@1 under a fixed training cost.
%
HM[$\mathcal{R},\mathcal{M}$] or HM[$\mathcal{R},g_\mathsf{LGA}$] can reach an
even higher ERS, but are excluded from comparison due to significant drop in
R@1.
%

@@

It \emph{should} be noted that the $L_\text{ICS}$ term improves 
robustness against most attacks involved in ERS, but also increases the
tendency to collapse (observed during TMA~\cite{flowertower} attack --
high cosine similarity between two arbitrary benign examples).
%
In some cases (\eg, on SOP), the robustness drop \emph{w.r.t} TMA may
neutralize the ERS gain from other attacks.
